---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Plotting functional responses

## Plotting replicates separately

```{r}
#### Code for functional response

# load libraries
library(tidyr)
library(stringi)
library(glue)
library(ggplot2)
library(data.table)

# some helper functions
source("code/functional_response.R")
```

Prepare to read data.

```{r}
# simulation type
sim_type <- c("obligate", "facultative", "foragers", "random")

# get the replicates
replicate <- stringr::str_pad(seq_len(3), pad = "0", width = 3)

# growth rates
regrowth <- c(0.001, 0.01, 0.03, 0.05)

# glue data folder names together
data <- crossing(
  sim_type,
  replicate,
  regrowth
)

# get folders
data$folder_path <- glue_data(.x = data,
                              'data/sim_{sim_type}_rep_{replicate}_\\
                                      gro_{regrowth}')
```

Summarise the data and read it in, using the helper functions.

```{r}
# get data
data$data_summary <- lapply(data$folder_path, function(x) {
  get_functional_response(
    data_folder = x,
    drivers = c("items", "total_agents")
  )
})

# unnest the data
data_plot <- unnest(data,
               cols = "data_summary")
```

Prepare the data for plotting.

```{r}
# set dt
setDT(data_plot)
data_plot <- split(data_plot, by = c("regrowth", "sim_type"))

# data_reg
data_reg <- data_plot[!stri_detect(names(data_plot), 
                                   fixed = "0.001")]
```

## Overall functional response

```{r}
fig_fun_response_total <- 
  lapply(data_reg, function(df) {
    ggplot(df)+
      geom_tile(aes(items, total_agents, 
                    fill = value + 1e-6))+
      facet_grid(replicate~variable)+
      # scico::scale_fill_scico(palette = "lajolla",
      #                         direction = -1,
      #                         limits = c(0, 0.25)
      #                         # breaks = c(1e-2, 1e0),
      #                         # labels = c("lower", "higher")
      # )+
      scale_fill_viridis_c(
        option = "B",
        limits = c(0.0001, 0.25)
      )+
      # coord_cartesian(xlim = c(0, 2.5),
      #             ylim = c(0, 0.15))+
      # coord_equal()+
      theme_minimal(base_size = 4)+
      theme(legend.position = "top",
            # panel.grid = element_blank(),
            plot.background = element_rect(fill = NA, colour = "grey"),
            legend.key.height = unit(2, units = "mm"),
            axis.title = element_text(face = "bold"),
            legend.title = element_text(face = "bold"))+
      labs(fill = "p.c.in.",
           x = "items",
           y = "agents",
           title = sprintf("sim_type = %s | regrowth = %f",
                           unique(df$sim_type), round(unique(df$regrowth), 2)))
  })
```

```{r}
# wrap and save
fig_fun_response_total <- patchwork::wrap_plots(fig_fun_response_total, 
                                          ncol = 3, nrow = 4)
fig_fun_response_total
ggsave(fig_fun_response,
       filename = "figures/fig_fun_response_overall.png",
       width = 12, height = 11)
```

### Averaging over replicates

```{r}
# bind data
data_reg <- rbindlist(data_reg)

# average over replicates and select only the highest growth rate
data_summary <- data_reg[regrowth == max(regrowth), 
                     list(value = mean(value)),
                     by = c("sim_type", "regrowth", 
                            "items", "total_agents", "variable")]

# split by sim type
data_summary <- split(data_summary, by = c("sim_type"))
```

```{r}
fig_fun_response <- 
  lapply(data_summary, function(df) {
    ggplot(df)+
      geom_tile(aes(items, total_agents, 
                    fill = value + 1e-6))+
      facet_grid(regrowth~variable)+
      # scico::scale_fill_scico(palette = "lajolla",
      #                         direction = -1,
      #                         limits = c(0, 0.33)
      #                         # breaks = c(1e-2, 1e0),
      #                         # labels = c("lower", "higher")
      # )+
      scale_fill_viridis_c(
        option = "B",
        limits = c(0.0001, 0.25)
      )+
      coord_cartesian(
        # xlim = c(0, 2.5),
                      ylim = c(0.00001, 0.15))+
      theme_minimal(base_size = 4)+
      theme(legend.position = "top",
            # panel.grid = element_blank(),
            plot.background = element_rect(fill = NA, colour = "grey"),
            legend.key.height = unit(2, units = "mm"),
            axis.title = element_text(face = "bold"),
            legend.title = element_text(face = "bold"))+
      labs(fill = "p.c.in.",
           x = "items",
           y = "agents",
           title = sprintf("sim_type = %s",
                           unique(df$sim_type)))
  })
```

```{r}
# wrap and save
fig_fun_response <- patchwork::wrap_plots(fig_fun_response)
fig_fun_response
ggsave(fig_fun_response,
       filename = "figures/fig_fun_response_avg.png",
       width = 12, height = 6)
```

## Functional response: Klepts ~ foragers

```{r}
# get data
data$data_summary <- lapply(data$folder_path, function(x) {
  get_functional_response(
    data_folder = x,
    drivers = c("klepts", "foragers")
  )
})

# unnest the data
data_plot <- unnest(data,
               cols = "data_summary")
setDT(data_plot)
```

### Average over replicates

```{r}
# average over replicates and select only the highest growth rate
data_summary <- data_plot[regrowth == max(regrowth), 
                     list(value = mean(value)),
                     by = c("sim_type", 
                            "klepts", "foragers", "variable")]

# remove simulation type foragers and random
data_summary <- data_summary[sim_type %in% c("facultative", "obligate"), ]

# split by sim type
data_summary <- split(data_summary, by = c("sim_type"))
```

```{r}
fig_fun_response <- 
  lapply(data_summary, function(df) {
    ggplot(df)+
      geom_tile(aes(foragers, klepts, 
                    fill = value + 1e-6))+
      geom_abline(slope = 1, lwd = 0.2)+
      facet_grid(~variable)+
      # scico::scale_fill_scico(palette = "lajolla",
      #                         direction = -1,
      #                         limits = c(0, 0.33)
      #                         # breaks = c(1e-2, 1e0),
      #                         # labels = c("lower", "higher")
      # )+
      scale_fill_viridis_c(
        option = "A",
        limits = c(0.0001, 0.33)
      )+
      coord_cartesian(
        xlim = c(0, 0.06),
        ylim = c(0, 0.06))+
      theme_minimal(
        base_size = 4
        )+
      theme(legend.position = "top",
            # panel.grid = element_blank(),
            plot.background = element_rect(fill = NA, colour = "grey"),
            legend.key.height = unit(2, units = "mm"),
            axis.title = element_text(face = "bold"),
            legend.title = element_text(face = "bold"))+
      labs(fill = "p.c.in.",
           # x = "items",
           # y = "agents",
           title = sprintf("sim_type = %s",
                           unique(df$sim_type)))
  })
```

```{r}
# wrap and save
fig_fun_response <- patchwork::wrap_plots(fig_fun_response)
fig_fun_response
ggsave(fig_fun_response,
       filename = "figures/fig_fun_response_strategy.png",
       width = 12, height = 3)
```

## Functional response: Foragers ~ items

```{r}
# get data
data$data_summary <- lapply(data$folder_path, function(x) {
  get_functional_response(
    data_folder = x,
    drivers = c("items", "foragers")
  )
})

# unnest the data
data_plot <- unnest(data,
               cols = "data_summary")
setDT(data_plot)
```

### Average over replicates

```{r}
# average over replicates and select only the highest growth rate
data_summary <- data_plot[regrowth == max(regrowth), 
                     list(value = mean(value)),
                     by = c("sim_type", 
                            "items", "foragers", "variable")]

# remove simulation type foragers and random
# data_summary <- data_summary[sim_type %in% c("facultative", "obligate"), ]

# split by sim type
data_summary <- split(data_summary, by = c("sim_type"))
```

```{r}
fig_fun_response <- 
  lapply(data_summary, function(df) {
    ggplot(df)+
      geom_tile(aes(items, foragers,
                    fill = value + 1e-6))+
      # geom_abline(slope = 1, lwd = 0.2)+
      facet_grid(~variable)+
      # scico::scale_fill_scico(palette = "lajolla",
      #                         direction = -1,
      #                         limits = c(0, 0.33)
      #                         # breaks = c(1e-2, 1e0),
      #                         # labels = c("lower", "higher")
      # )+
      scale_fill_viridis_c(
        option = "A",
        limits = c(0.0001, 0.33)
      )+
      # coord_cartesian(
      #   xlim = c(0, 0.06),
      #   ylim = c(0, 0.06))+
      theme_minimal(
        base_size = 4
        )+
      theme(legend.position = "top",
            # panel.grid = element_blank(),
            plot.background = element_rect(fill = NA, colour = "grey"),
            legend.key.height = unit(2, units = "mm"),
            axis.title = element_text(face = "bold"),
            legend.title = element_text(face = "bold"))+
      labs(fill = "p.c.in.",
           # x = "items",
           # y = "agents",
           title = sprintf("sim_type = %s",
                           unique(df$sim_type)))
  })
```

```{r}
# wrap and save
fig_fun_response <- patchwork::wrap_plots(fig_fun_response)
fig_fun_response
ggsave(fig_fun_response,
       filename = "figures/fig_fun_response_foragers.png",
       width = 12, height = 6)
```