---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Landscape effects

```{r}
# to handle data and plot
library(data.table)
library(glue)

library(ggplot2)
library(colorspace)
library(patchwork)
```

## Read node weight evolution

```{r}
# read back in
data <- fread("data_sim/results/data_early_0_100_weight_evolution.csv")
# data[, folder_path := stringr::str_replace(folder_path, "data", "data_sim")]

# select growth rates of 0.001, 0.01, 0.1, 0.25
focus_r <- c(0.001, 0.01, 0.05)
data <- data[regrowth %in% focus_r, ]

# handle weight value ranges and use UPPER bound
data[, weight_num :=
  stringi::stri_extract_last(weight_value,
    regex = "[-0-9]+\\.\\d{2}"
  )]
# assign numeric
data[, weight_num := as.numeric(weight_num)]

# remove random sim
data <- data[sim_type != "random", ]
```

## Prepare summary data

Handler preference

```{r}
# get positive weights for handlers (weight 3)
wt_handler <- data[weight_id == 3 &
  weight_num > 0 &
  regrowth == 0.01 &
  sim_type != "random", ]

# sum proportions
wt_handler <- wt_handler[, list(pref_handlers = sum(weight_prop)),
  by = c("sim_type", "replicate", "regrowth", "gen")
]
```

Kleptoparasite bias for fixed strategy

```{r}
klept_bias <- data[weight_id == 5 & weight_num < 0 & sim_type != "facultative", ]
klept_bias <- klept_bias[, list(klept_strategy = sum(weight_prop)),
  by = c("sim_type", "replicate", "regrowth", "gen")
]
```

Handler strategy

```{r}
handler_strategy <- data[sim_type == "facultative" & weight_id == 7 & weight_num < 0, ]
handler_strategy <- handler_strategy[, list(klept_strategy = sum(weight_prop)),
  by = c("sim_type", "replicate", "regrowth", "gen")
]
```

### Merge weight strategy

```{r}
data_wt <- rbindlist(list(klept_bias, handler_strategy))
```

## Read p clueless

```{r}
# focus r
focus_r <- c(0.01)

# read clueless data
data <- fread("data_sim/results/data_p_clueless.csv")
data[, path := NULL]
data <- data[regrowth %in% focus_r, ]
data[, sim_type := ifelse(sim_type == "forager", "foragers", sim_type)]

# remove v1
data[, V1 := NULL]

# remove random
data <- data[sim_type != "random"]
```


## Read proportion strategy data

```{r}
# get data
data_strat <- fread("data_sim/results/data_strategy_gen.csv")
data_strat <- data_strat[sim_type != "random"]

# subset for klept prop
data_strat <- data_strat[variable == "stealing" &
  regrowth %in% focus_r, ]

# remove zero vlaues for stealing in foragers only
data_strat <- data_strat[!(sim_type == "foragers" & variable == "stealing"), ]

# dcast
data_strat <- dcast(data_strat, sim_type + replicate +
  regrowth + gen + pop_fitness + conflicts ~ variable,
value.var = "value"
)

# join with land data
data_strat <- merge(data_strat, data,
  by = c("gen", "replicate", "regrowth", "sim_type"),
  all.y = TRUE
)

# join with data_wt
data_strat <- merge(data_strat, data_wt)

# join with handler preference
data_strat <- merge(data_strat, wt_handler)

# melt
data <- copy(data_strat)

data <- melt(data,
  id.vars = c(
    "gen", "replicate",
    "regrowth", "sim_type"
  )
)

# set factor order
data$sim_type <- factor(data$sim_type,
  levels = c("foragers", "obligate", "facultative")
)

# remove variables
data <- data[variable %in%
  c("stealing", "p_clueless", "klept_strategy", "pref_handlers"), ]

#
# # split data
data <- split(data, by = "sim_type")
```

```{r}
# make subplots
subplots <- lapply(data, function(df) {
  if (unique(df$sim_type) == "foragers") {
    x_lim <- c(0, 100)
    df <- df[gen <= 100, ]
    df[variable == "klept_strategy", "value"] <- NA
  } else {
    x_lim <- c(0, 50)
    df <- df[gen <= 50, ]
  }

  ggplot(df) +
    geom_path(aes(gen, value,
      col = variable,
      group = interaction(replicate, variable)
    ), size = 0.4) +
    scale_colour_manual(
      values = c(
        p_clueless = "grey40",
        stealing = "red",
        klept_strategy = "darkorange",
        pref_handlers = "steelblue"
      ),
      labels = c(
        p_clueless = "Clueless plateaus",
        stealing = "Time stealing",
        klept_strategy = "Prop. klept.",
        pref_handlers = "Pref. handler"
      ),
      breaks = c(
        "pref_handlers", "klept_strategy",
        "stealing", "p_clueless"
      )
    ) +
    scale_y_continuous(
      breaks = seq(0, 1, 0.25),
      labels = c("0", "0.25", "0.5", "0.75", "1")
    ) +
    coord_cartesian(
      xlim = x_lim,
      ylim = c(0, 1),
      expand = F
    ) +
    kleptomoveMS::theme_custom(grid = T, base_size = 8) +
    labs(
      x = "Generation",
      y = "Proportion",
      colour = NULL
    ) +
    guides(colour = guide_legend(nrow = 1, byrow = TRUE))
})

# work on adding lines at different levels
```

## Show landscape for each sim type

Here we show a landscape with and without clues at 1, 10, and 40th generation for $r_{max}$ = 0.01.

### Items landscape

```{r}
# list folders
paths <- list.dirs("data_sim/for_landscape/", recursive = F)

# select gens
gens_for_figure <- stringr::str_pad(c(1, 10, 50), width = 5, pad = "0")

# get paths for files
landscape_data <- CJ(
  gen = gens_for_figure,
  path = paths
)

# add sim_type
landscape_data[, sim_type := rep(c("facultative", "foragers", "obligate"), 3)]

# get paths
landscape_data$image <- glue_data(landscape_data, "{path}/{gen}.png")

# get data
landscape_data$data <- lapply(landscape_data$image,
  kleptomoveMS::read_landscape,
  layer = 4,
  crop_dim = 60,
  type = "items"
)

# convert gen to numeric
landscape_data[, gen := as.numeric(gen)]

# unlst
landscape_items <- landscape_data[, unlist(data, recursive = F),
  by = c("sim_type", "gen")
]
```

### Gradient landscape


```{r}
# get data
landscape_data$data <- lapply(landscape_data$image,
  kleptomoveMS::read_landscape,
  layer = 4,
  crop_dim = 60,
  type = "gradient"
)
# unlst
landscape_gradient <- landscape_data[, unlist(data, recursive = F),
  by = c("sim_type", "gen")
]
```

### Merge landscapes

```{r}
# landscape overall
landscape <- (landscape_gradient)

# melt
landscape <- melt(landscape, id.vars = c("sim_type", "gen", "x", "y"))

# split by sim_type
landscape <- split(landscape, by = c("sim_type", "variable"))
```


### Plot landscape

```{r}
subplot_land <- lapply(landscape, function(df) {
  pal <- sequential_hcl(5, palette = "Terrain", rev = T)[4]
  # set palette
  if (unique(df$variable) == "items") {
    pal <- viridis::viridis(5, direction = -1)
  }

  ggplot(df) +
    geom_tile(aes(x, y, fill = (value)),
      show.legend = F
    ) +
    facet_grid(~gen, labeller = label_both) +
    scale_fill_gradientn(
      colours = pal,
      na.value = ifelse(unique(df$variable) == "items", "white", "grey20"),
      limits = c(0.7, NA)
    ) +
    coord_equal(expand = F) +
    kleptomoveMS::theme_custom(landscape = T, base_size = 8) +
    theme(
      axis.text = element_blank(),
      axis.title = element_blank()
    )
})

# arrange order
sim_types <- c("foragers", "obligate", "facultative")

# figure names
fignames <- c(glue("{sim_types}.gradient"))
# arrange plots in order
subplot_land <- subplot_land[fignames]
```


## Figure 6

```{r}
# make figure 6
figure_8 <-
  wrap_plots(append(
    subplots[c(
      "foragers",
      "obligate", "facultative"
    )],
    subplot_land
  ), byrow = F, ncol = 2) +
    plot_layout(guide = "collect") +
    plot_annotation(
      tag_levels = "A"
    ) &
    theme(
      plot.tag = element_text(
        face = "bold",
        size = 12
      ),
      legend.position = "top"
    )

ggsave(
  figure_8,
  height = 160,
  width = 170,
  units = "mm",
  filename = "figures/fig_08.png"
)
```

