---
output:
  pdf_document: default
editor_options:
  chunk_output_type: console
---

# Individual Differences in Movement Strategies in Scenarios 2 and 3

```{r }
library(data.table)

library(ggplot2)
library(patchwork)
library(colorspace)
```

```{r}
# load relative preferences
data_pref = fread("data/results/data_rel_pref.csv")
data_pref = data_pref[gen == 950,]

# no foragers
data_pref = data_pref[sim_type %in% c("obligate", "facultative")]

data_pref$sim_type = factor(data_pref$sim_type, 
  levels = c("obligate", "facultative"))
```

```{r}
fig_variation = ggplot(data_pref)+
  geom_abline(
    intercept = c(0, 1, -1),
    slope = c(0, -1, 1),
    lty = 2,
    size = 0.4,
    col = "grey"
  )+
  geom_jitter(
    aes(
      sP, sH, 
      fill = comp_strat
    ),
    shape = 21,
    size = 3,
    alpha = 0.5
  ) +
  scale_fill_discrete_qualitative(
    palette = "Set 2",
    order = c(2, 3, 1),
    labels = c(
      "Sc. 3: All consumers",
      "Sc. 2: Foragers",
      "Sc. 2: Kleptoparasites"
    )
  )+
  coord_cartesian(
    xlim = c(0, 0.03)
  ) +
  theme_test(
    base_size = 10
  )+
  theme(
    strip.background = element_blank(),
    strip.text = element_text(
      face = "italic"
    ),
    legend.position = "top"
  )+
  facet_grid(
    cols = vars(rep),
    rows = vars(sim_type),
    labeller = labeller(
      rep = function(x) glue::glue("Rep: {x}"),
      sim_type = c(
        "obligate" = "Scenario 2",
        "facultative" = "Scenario 3"
      )
    )
  )+
  labs(
    x = "sP: Prey-item preference",
    y = "sH: Handler preference",
    fill = NULL
  )+
  guides(
    fill = guide_legend(
      override.aes = list(
        alpha = 1
      )
    )
  )

# save figure
ggsave(
  fig_variation,
  filename = "supplement/figures/fig_small_scale_variation.png",
  height = 4,
  width = 6
)
```

![**Small-scale individual variation may be hidden by primary drivers of behaviour**. Across simulation replicates ($r_{max}$ = 0.01), populations in scenarios 2 and 3 do show small-scale individual variation in preference for prey density cues ($s_P$). This variation is unlikely, in our model, to lead to functional differences in movement paths, but may cause very small emergent differences in model implementations of movement over a continuous space. It is key therefore to measure variation, and the relative contribution of such variation, along multiple axes of behaviour when studying the functional consequences of individual differences.]("figures/fig_small_scale_variation.png")

\newpage
