---
output: html_document
editor_options:
  chunk_output_type: console
---

# Get evolutionary dynamics

```{r }
# load libraries
library(data.table)
library(stringr)
# some helper functions
library(kleptomoveMS)
```

Prepare data paths.

```{r}
Prepare the data paths.

```{r }
# read paths
paths <- list.dirs("data_sim/", recursive = F)
paths <- paths[grep("rep_", paths)]

# make df
data = CJ(
  path = paths
)

# get replicate
data[, rep := as.numeric(
  stringr::str_extract_all(path, "rep_(\\d{3})") |> 
    stringr::str_extract_all("\\d{3}")
)]

# get sim type
data[, sim_type := stringr::str_extract(
  path, "obligate|facultative|foragers|random"
 ) 
]

data[, regrowth := as.numeric(str_extract(path, "(0\\.\\d+)"))]
```

```{r }
# get strategy, fitness and conflicts over gens
data[, summary_data := lapply(
  path,
  get_strategy_gen
)]
```

```{r }
# unlist
data <- data[, unlist(summary_data, recursive = F),
  by = c("sim_type", "rep", "regrowth")
]
```

```{r }
# save data
fwrite(data, file = "data_sim/results/data_strategy_gen.csv")
```

