---
output: html_document
editor_options:
  chunk_output_type: console
---

# Get relative preferences

These are the relative preferences that determine movement strategies.

```{r }
# load libs
library(data.table)
library(stringr)
devtools::load_all()
```

Prepare data paths.

```{r}
# read paths
paths <- list.dirs("data_sim/", recursive = F)
paths <- paths[grep("rep_", paths)]

# make df
data = CJ(
  path = paths
)

# get replicate
data[, rep := as.numeric(
  stringr::str_extract_all(path, "rep_(\\d{3})") |> 
    stringr::str_extract_all("\\d{3}")
)]

# get sim type
data[, sim_type := stringr::str_extract(
  path, "obligate|facultative|foragers|random"
 ) 
]

data[, regrowth := as.numeric(str_extract(path, "(0\\.\\d+)"))]

# filter for focus regrowth
data = data[regrowth == 0.01,]
```

## Relative preference for movement cues

Read scaled movement weights from 2500 individuals in each simulation from generations 1, 10, 30, 100, and 950.

```{r}
# make a copy
data_rel_pref = copy(data)

# get relative preferences using the function get_scaled_move_prefs
data_rel_pref[, rel_pref := lapply(
  X = path, 
  
  # apply this function over all the paths
  FUN = get_scaled_move_prefs, 
  
  # these are arguments to get_scaled_move_prefs
  gens = c(1, 10, 30, 100, 300, 950), 
  n_agents = 2500
)]

# unlist (un-compress) the data to make an ordinary data.frame
data_rel_pref = data_rel_pref[, unlist(rel_pref, recursive = F),
  by = list(sim_type, rep, regrowth)
]

# assign strategy
data_rel_pref[, comp_strat := fifelse(
  sim_type == "obligate", comp_strat, "consumer"
  )
]

fwrite(data_rel_pref, file = "data/results/data_rel_pref.csv")
```

## Evolution of handler tracking

Get the preference for moving towards handlers, i.e., successful foragers, sub-divided by competitive strategy.
This is done by processing each simulation replicate using `get_pref_handler_by_strat`, which is defined and documented in `R/fun_syndrome.R`

The naming refers to the idea that certain behaviours may be correlated, forming a 'syndrome'.

```{r}
# run the function over each simulation replicate
syndrome_data <- lapply(
  X = data$path, 
  
  # apply this function, based around get_pref_handler_by_strat
  FUN = function(path) {
    get_pref_handler_by_strat(
      data_folder = path,
      generations = unique(
        seq(1, 999, 2)
      ),
      weight_comp_strat = 5,
      weight_of_interest = c(
        handler_pref = 3
      ),
      handler_pref_by_strategy = TRUE
  )
})

# make a copy
data_si_strategy = copy(data)

# add to data
data_si_strategy$syndrome_data <- syndrome_data

# unlist
data_si_strategy <- data_si_strategy[, unlist(syndrome_data, recursive = FALSE),
  by = c("sim_type", "rep", "regrowth")
]

# combine proportions and counts for all but the scenario 2 obligate case
data_si_strategy[, comp_strat := fifelse(
  sim_type == "obligate", comp_strat, "consumer"
)]

data_si_strategy = data_si_strategy[, list(
  prop_handler_pref = sum(prop_handler_pref)
),
by = c(
  "sim_type", "rep", "regrowth", 
  "comp_strat", "handler_pref", "gen"
)
]

# save data
fwrite(data_si_strategy, file = "data/results/data_handler_tracking_by_strategy.csv")
```

## Relative preferences for competitive strategies

```{r}
data_comp_pref = copy(data)
data_comp_pref = data_comp_pref[sim_type == "facultative",]

data_comp_pref[, comp_pref := lapply(
  path, get_scaled_move_prefs, 
  weights = c(5,6,7,8),
  gens = c(1, 10, 30, 100, 300, 950), n_agents = 2500
)]

data_comp_pref = data_comp_pref[, unlist(comp_pref, recursive = F),
  by = list(sim_type, rep, regrowth)
]

fwrite(data_comp_pref, file = "data_sim/results/data_comp_pref.csv")
```

```{r}
data_comp_pref = fread("data_sim/results/data_comp_pref.csv")
# data_comp_pref = data_comp_pref[gen == 950,]

# choice under different number of prey and handlers
data_comp_expand = tidyr::crossing(
  data_comp_pref,
  food = seq(0, 5, 1),
  handlers = seq(0, 5, 1)
)
setDT(data_comp_expand)

# calculate decision
data_comp_expand[, choice := (wt_7 * handlers) + (wt_8 * food) >= wt_5]
data_comp_expand[, choice := fifelse(choice, "forage", "steal")]

# summarise decision
data_comp_prop = data_comp_expand[, .N, 
  by = c("gen", "food", "handlers", "choice", "rep")
]

data_comp_prop = dcast(
  data_comp_prop,
  gen + food + handlers + rep ~ choice,
  value.var = "N"
)

# save data
fwrite(data_comp_prop, "data_sim/results/data_sc3_comp_choice.csv")
```